Towards Cloud Bursting for Extreme Scale Supercomputers\\ (Unrefereed Workshop Manuscript)

### 2014-07-01 paper/src/2_motivation.tex
finish

To solve this problem, we propose our I/O burst buffer architecture, since usually Internet throuhput is the bottleneck, by using parallel I/O and cacheing file in I/O buffer nodes, we can fully utilize the Internet bandwidth as well as avoid frequently transfering file between two systems, hence achieve a high I/O throughput.
Althought using I/O buffer can increase I/O throughput, reduce the execution time and cost, I/O buffer nodes will be charged for usage, also a better instance will cost more than a normal one, there will be a trade-off between I/O performance and monetary cost.
Moreover, the instance choice, number of I/O nodes depends on supercomputer and pulic cloud environment, in our following section, we will provide a performance modele

@@

\subsection{(Current Section 2)}
\kento{Please fit the below sentences to the above sections with additional explanations}

@@

%using I/O burst buffer requires addtional nodes running on public cloud and means more cost, also like Amazon EC2, public cloud usually provides various instance types with different specification, using which instance type also will affect both cost and performance.
%We provide a cost-based model to determine 
Fig.\ref{point to point connection AMAZON} shows the Ethernet throughput inside Amazon EC2 taken by using Iperf, although we only show the result up to 8 pairs of nodes, each node achieved only 135MB/s (1GBit/s), the influence between nodes is extremely small, figure shows a perfect linear line also a strong scalability.
since when we running the benchmark, many other users were also running applications on Amazon, so we can assume that highest throughput 1GB/s (8Gbit/s) shown in Fig.~\ref{point to point connection AMAZON} is not the maximum bandwidth of Ethernet in Amazon EC2.
Comparing Fig.~\ref{point to point connection AMAZON} with Fig.~\ref{throughput AMAZON to OURLAB} and Fig.~\ref{point to point connection LAB}, Ethernet throughput is much higher than Internet, it shows that our solution, by using I/O buffer nodes can achieve a higher Ethernet throughput than Internet.
%Since we can achieve a high interconnection throughput inside a system (HPC system, public cloud), we consider use some nodes as a buffer nodes, using a buffer queue to buffer I/O data and achieve a high throughput.

Although there are some studies about workflow optimization and  balance\cite{Workload}, Since data transfer rate is extremely low in Internet compared with interconnection network and data size processed is extremely large, user do not want to settle their nodes across two systems, so in this model, we just consider the situation that all nodes used for the same job are allocated in the same system.

>>>>

However, when we look at Ethernet throughput inside Amazon as Fig.\ref{point to point connection AMAZON} shows, although we only show the result up to 8 pairs of nodes, each node achieved only 135MB/s (1GBit/s), the influence between nodes is extremely small, figure shows a perfect linear line also a strong scalability.
since when we running the benchmark, many other users were also running applications on Amazon, so we can assume that highest throughput 1GB/s (8Gbit/s) shown in Fig.~\ref{point to point connection AMAZON} is not the maximum bandwidth of Ethernet in Amazon EC2 .
Comparing Fig.~\ref{point to point connection AMAZON} with Fig.~\ref{throughput AMAZON to OURLAB} and Fig.~\ref{point to point connection LAB}, Ethernet throughput is much higher than Internet, it shows that our solution, by using I/O buffer nodes can achieve a higher Ethernet throughput than Internet.

To solve this problem, we propose our I/O burst buffer architecture, since usually Internet throuhput is the bottleneck, by using parallel I/O and cacheing file in I/O buffer nodes, we can fully utilize the Internet bandwidth as well as avoid frequently transfering file between two systems, hence achieve a high I/O throughput.
Althought using I/O buffer can increase I/O throughput, reduce the execution time and cost, I/O buffer nodes will be charged for usage, also a better instance will cost more than a normal one, there will be a trade-off between I/O performance and monetary cost, we will introduce a throughput-based model and a cost-based model to predict the throughput and overall cost.
%Moreover, the instance choice, number of I/O nodes depends on supercomputer and pulic cloud environment, in our following section, we will provide a performance modele

@@

%\subsection{(Current Section 2)}
\kento{Please fit the below sentences to the above sections with additional explanations}

@@

%using I/O burst buffer requires addtional nodes running on public cloud and means more cost, also like Amazon EC2, public cloud usually provides various instance types with different specification, using which instance type also will affect both cost and performance.
%We provide a cost-based model to determine 
%Since we can achieve a high interconnection throughput inside a system (HPC system, public cloud), we consider use some nodes as a buffer nodes, using a buffer queue to buffer I/O data and achieve a high throughput.

%Although there are some studies about workflow optimization and  balance\cite{Workload}, Since data transfer rate is extremely low in Internet compared with interconnection network and data size processed is extremely large, user do not want to settle their nodes across two systems, so in this model, we just consider the situation that all nodes used for the same job are allocated in the same system.

### 2014-07-01 paper/src/4_model.tex
finish

The throughput-based model, cost-based model and buffer queue write back model are described in this section.
As we explained in the previous section, two-side buffer model is better than one-side buffer model, in the following section, we will use two-side buffer model as our read from and write back model in I/O burst buffer
\kento{this sentences should be in the previsou section}.

The throughput-based model compares throughput with and without I/O burst buffer, cost-based model compare cost with and without I/O burst buffer, and buffer queue write back model shows the situation that I/O buffer queue will be full. 
We make definitions shows in Table \ref{definition} in order to describe our model.
\begin{table}[tb]
	\caption{Definition of parameters}
	\label{definition}
\begin{tabular}{|p{3cm}|p{5cm}|}
	\hline
	$c_1,c_2$&Numbers of computing nodes in system 1 and system 2\\\hline
	$n_1, n_2$&Numbers of I/O buffer nodes in system 1 and system 2.\\\hline
	$m_1,m_2$&Available memory size for each I/O node in system 1 and 2, also the maximum buffer size will be $n_1\times m_1$ and $n_2\times m_2$\\\hline
	$D_1(n_2),D_2(n_2)$&Throughput when $n_2$($n_1$) I/O nodes in system 1 (system 2) connect to storage in the other system directly, here we assume I/O nodes and computing nodes in each system have the same Internet connection speed.\\\hline% have Internet connection.\\\hline
	$I(n_1,n_2)$& 	Internet throughput using $n_1,n_2$ nodes respectively, since overall Internet throughput is affected by number of nodes involved in connection.\\\hline
	$E_1(n_1), E_2(n_2)$&Interconnection network throughput in system 1 and 2, although interconnection throughput is also affected by numbers of I/O nodes and computing nodes, numbers of users will running application on different number of computing nodes.\\\hline
	%, it is difficult to compute each throughput, so here we use $E_1(n_1)$ to refer to limitation of maximum throughput of interconnection network in system 1 with $n_1$ I/O nodes, likely ,$E_2(n_2)$ is limitation of maximum throughput of interconnection network in system 2 with $n_2$ I/O nodes.
	$M_1(n_1),M_2(n_2)$& Throughput of connection between storage and $n_1$ I/O nodes in system 1 and storage and $n_2$ I/O nodes in system 2.\\\hline
	$C_i\_Money(T)$& Cost for standard node in system $i$ for $T$ time usage\\\hline
	%and cost for node in system 1 is $C_2\_Money(T)$ for $T$ time usage, and since I/O nodes may use a better network, 
	$C_i\_High\_Money(T)$ &I/O nodes in system $i$ for $T$ time usage, since I/O nodes may use a better network condition, we assume it will cost more than normal nodes.\\\hline
\end{tabular}
\end{table}

\subsection{Throughput-based Model}
%There are many facts will affect throughput of Internet, so here a moniter is used to evaluate throughput between 
In the case of direct I/O \kento{What is direct I/O. I think it means direct connection mode in Section 3, but no explanation at all}, computing nodes connect to storage in another system directly, there is only one data transfer, so throughput \kento{read ? or write ? or both ?} will be:%there are two data transfers: computation nodes to I/O buffer nodes in system 2, I/O buffer nodes in system 2 to storage in system 1, so throughput will be:
\begin{equation}
	\text{thr}_{\text{direct}}=D_1(c_2) \label{throughput1}
\end{equation}

When using I/O burst buffer, there will be three data transfers: computation nodes to I/O buffer nodes in system 2, I/O buffer nodes in system 2 to I/O buffer nodes in system 1, I/O buffer nodes in system 1 to storage in system 1, throughput \kento{write ? and read ?. Explain how the buffer queue works (1) if buffer space is avaialble for write, (2) reading data is in the buffer queue. We need expian this in both previous section and in here} will be:
\begin{eqnarray}
	\text{thr}_{\text{I/O buffer}}=\begin{cases}
		E_2(n_2) &\text{buffer queue available}\\ 
	\min\{M_1(n_1),I(n_1,n_2),E_2(n_2)\} &\text{buffer queue full}
	\end{cases} \label{throughput2}
\end{eqnarray}

In this throughput-based model, these two throughputs are evaluated, and a switch is based on these two values:
\kento{Why do you swithches between direct I/O and burst buffer?}
\begin{equation}
	\begin{cases}
		\text{thr}_{\text{direct}} \geq \text{thr}_{\text{I/O buffer}} & \text{use direct I/O}\\
		\text{thr}_{\text{direct}} < \text{thr}_{\text{I/O buffer}} & \text{use I/O burst buffer}
	\end{cases}
\end{equation}

@@

\subsection{Cost-based Model}
\kento{Again, it's hard to understand due to lack of information. Please read carfully over and over again and add more explanation like in the above}
In the case of cost-based model, we consider the overall cost for using direct I/O and using I/O burst buffer. Although using I/O burst buffer will cost for I/O nodes, higher throughput can reduce execution time and also overall cost.
using \ref{throughput1},and \ref{throughput2} total time for transferring unit size of data can be compute as:

\begin{equation}
	\begin{cases}
		T_1=\frac{1}{D_1(c_2)} & \text{direct}\\
		T_2=\frac{1}{\min\{M_1(n_1),I(n_1,n_2),E_2(n_2)\}} &\text{buffer queue available}\\
		T_3=\frac{1}{E_2(n_2)} &\text{buffer queue full}
	\end{cases}
\end{equation}

here we compute cost by using $T_1,T_2,T_3$:
\begin{equation}
	\text{cost}_\text{direct}=c_2\times C_2\_Money(T_1)+n_2\times C_2\_High\_Money(T_1)
\end{equation}
\kento{According to the difinition of $C_i\_Money(T)$ and $T_i$, the above model seems to be wrong. Please read carfully the model is correct}
\begin{align}
	\text{cost}_\text{I/O buffer}=\\\begin{cases}
				c_2\times C_2\_Money(T_2)+n_1\times C_1\_High\_Money(T_2)+n_2\times C_2\_High\_Money(T_2)&\text{buffer queue available}\\
				c_2\times C_2\_Money(T_3)+n_1\times C_1\_High\_Money(T_3)+n_2\times C_2\_High\_Money(T_3) &\text{buffer queue full}
\end{cases}
\end{align}

In this cost-based model, these two cost are evaluated, and a switch is based on these two values:
\begin{equation}
	\begin{cases}
		\text{cost}_{\text{direct}} \geq \text{cost}_{\text{I/O buffer}} & \text{use direct I/O}\\
		\text{cost}_{\text{direct}} < \text{cost}_{\text{I/O buffer}} & \text{use I/O burst buffer}
	\end{cases}
\end{equation}

@@

After that, since buffer queue is full, I/O server can not send more data to I/O buffer nodes, have to block any read and write request since that.
In this case, jobs running on public cloud have to be moved back to original system until buffer queue is empty
\kento{Why ??}.

>>>>

Since the instance type choice, Ethernet condition, Internet condition will affect the actual I/O throughput between two system, we introduce a throughput-based model, cost-based model and buffer queue write back model used to predict throughput, overall cost and in buffer rate when use I/O burst buffer and direct I/O, and using these predict model to make decision like which type of instance should use, and how many I/O nodes is needed in a particular cases.
\kento{this sentences should be in the previsou section}.

The throughput-based model compares throughput with and without I/O burst buffer, cost-based model compare cost with and without I/O burst buffer, and buffer queue write back model shows the situation that I/O buffer queue will be full.
We make definitions shows in Table \ref{definition} in order to describe our model.
\begin{table}[tb]
	\caption{Definition of parameters}
	\label{definition}
\begin{tabular}{|c|p{5cm}|}
	\hline
	$c_1,c_2$&Numbers of computing nodes in system 1 and system 2\\\hline
	$n_1, n_2$&Numbers of I/O buffer nodes in system 1 and system 2.\\\hline
	$m_1,m_2$&Available memory size for each I/O node in system 1 and 2, also the maximum buffer size will be $n_1\times m_1$ and $n_2\times m_2$\\\hline
	$D_1(n_2),D_2(n_2)$&Throughput when $n_2$($n_1$) I/O nodes in system 1 (system 2) connect to storage in the other system directly, here we assume I/O nodes and computing nodes in each system have the same Internet connection speed.\\\hline% have Internet connection.\\\hline
	$I(n_1,n_2)$& 	Internet throughput using $n_1,n_2$ nodes respectively, since overall Internet throughput is affected by number of nodes involved in connection.\\\hline
	$E_1(n_1), E_2(n_2)$&Interconnection network throughput in system 1 and 2, although interconnection throughput is also affected by numbers of I/O nodes and computing nodes, numbers of users will running application on different number of computing nodes.\\\hline
	%, it is difficult to compute each throughput, so here we use $E_1(n_1)$ to refer to limitation of maximum throughput of interconnection network in system 1 with $n_1$ I/O nodes, likely ,$E_2(n_2)$ is limitation of maximum throughput of interconnection network in system 2 with $n_2$ I/O nodes.
	$M_1(n_1),M_2(n_2)$& Throughput of connection between storage and $n_1$ I/O nodes in system 1 and storage and $n_2$ I/O nodes in system 2.\\\hline
	$C_iM(T)$& Cost for standard node in system $i$ for $T$ time usage\\\hline
	%and cost for node in system 1 is $C_2\_Money(T)$ for $T$ time usage, and since I/O nodes may use a better network, 
	$C_iHM(T)$ &I/O nodes in system $i$ for $T$ time usage, since I/O nodes may use a better network condition, we assume it will cost more than normal nodes.\\\hline
\end{tabular}
\end{table}

\subsection{Throughput-based Model}
%There are many facts will affect throughput of Internet, so here a moniter is used to evaluate throughput between 
First we consider direct I/O, computing nodes read from and write back to storage in another system directly.
In the case of direct I/O \kento{What is direct I/O. I think it means direct connection mode in Section 3, but no explanation at all}, computing nodes connect to storage in another system directly, there is only one data transfer, so both read and write throughput \kento{read ? or write ? or both ?} will be:%there are two data transfers: computation nodes to I/O buffer nodes in system 2, I/O buffer nodes in system 2 to storage in system 1, so throughput will be:
\begin{equation}
	\text{thr}_{\text{direct}}=D_1(c_2) \label{throughput1}
\end{equation}

When using I/O burst buffer, there will be three data transfers: computation nodes to I/O buffer nodes in system 2, I/O buffer nodes in system 2 to I/O buffer nodes in system 1, I/O buffer nodes in system 1 to storage in system 1, 
for reading, if required file is buffered in buffer queue, computing node can read data from buffer queue directly, then throughput will be:$E_2(n_2)$, similiarly, if buffer queue still have enough space for I/O data when issue a write request, computing nodes can write data to buffer queue, and throughput also will be:$E_2(n_2)$.

If required file is not buffered in buffer queue when issue a read request, or when issue a write request buffer queue is full, the throughput will be:$\min\{M_1(n_1),I(n_1,n_2),E_2(n_2)$, since for read request, file need to be read from storage in another system Internet, and for write request, it need to wait until buffer buffer write buffered file back the storage.
throughput \kento{write ? and read ?. Explain how the buffer queue works (1) if buffer space is avaialble for write, (2) reading data is in the buffer queue. We need expian this in both previous section and in here} here we summary them as:
\begin{eqnarray}
	\text{thr}_{\text{I/O buffer}}=\begin{cases}
		E_2(n_2) &\text{buffer queue available}\\ 
	\min\{M_1(n_1),I(n_1,n_2),E_2(n_2)\} &\text{buffer queue full or file miss}
	\end{cases} \label{throughput2}
\end{eqnarray}
Although we have two cases for each read and write request (in buffer or not in buffer), it is very difficult to predict the in buffer rate, since it will be affected by I/O size, Internet throughput, buffer queue size and so on.
\kento{Why do you swithches between direct I/O and burst buffer?}
%\begin{equation}
%	\begin{cases}
%		\text{thr}_{\text{direct}} \geq \text{thr}_{\text{I/O buffer}} & \text{use direct I/O}\\
%		\text{thr}_{\text{direct}} < \text{thr}_{\text{I/O buffer}} & \text{use I/O burst buffer}
%	\end{cases}
%\end{equation}

@@

\subsection{Cost-based Model}
\kento{Again, it's hard to understand due to lack of information. Please read carfully over and over again and add more explanation like in the above}
Although we may use I/O burst buffer to achieve a high I/O throughput and leading a decrease of execution time, and according to public cloud pay for usage policy, the cost for computing nodes may reduce, the relation between overall cost and I/O throughput can not be such simple, since I/O nodes will still charged for usage, and if we use a instance with high Ethernet condition in order to get a higher throughput, we may be charged for more money.

Here we provide a cost-based model in order to predict overall cost for using I/O burst buffer and direct I/O.
Like throughput-based model, cost will be affected by in buffer rate, but it depends on application and buffer queue size, and is very difficult to predict.
%In the case of cost-based model, we consider the overall cost for using direct I/O and using I/O burst buffer. Although using I/O burst buffer will cost for I/O nodes, higher throughput can reduce execution time and also overall cost.
According to \ref{throughput1},and \ref{throughput2} total time for transferring unit size of data can be compute as:

\begin{equation}
	\begin{cases}
		T_1=\frac{Data~size}{D_1(c_2)} & \text{direct}\\
		T_2=\frac{Data~size}{\min\{M_1(n_1),I(n_1,n_2),E_2(n_2)\}} &\text{buffer queue full or file miss}\\
		T_3=\frac{Data~size}{E_2(n_2)} &\text{buffer queue available}
	\end{cases}
\end{equation}

here we compute cost by using $T_1,T_2,T_3$:
\begin{equation}
	\text{cost}_\text{direct}=c_2\times C_2M(T_1)+n_2\times C_2HM(T_1)
\end{equation}
\kento{According to the difinition of $C_i\_Money(T)$ and $T_i$, the above model seems to be wrong. Please read carfully the model is correct}
\begin{align}
	\begin{cases}
		c_2\times C_2M(T_2)+n_1\times C_1HM(T_2)+n_2\times C_2HM(T_2)&\text{buffer queue available}\\
		c_2\times C_2M(T_3)+n_1\times C_1HM(T_3)+n_2\times C_2HM(T_3) &\text{buffer queue full}
	\end{cases}
\end{align}

%In this cost-based model, these two cost are evaluated, and a switch is based on these two values:
%\begin{equation}
%	\begin{cases}
%		\text{cost}_{\text{direct}} \geq \text{cost}_{\text{I/O buffer}} & \text{use direct I/O}\\
%		\text{cost}_{\text{direct}} < \text{cost}_{\text{I/O buffer}} & \text{use I/O burst buffer}
%	\end{cases}
%\end{equation}

@@

After that, since buffer queue is full, I/O server can not send more data to I/O buffer nodes, have to block any read and write request since that.
\kento{Why ??}.
